A cautionary note on the use of Ornstein Uhlenbeck and other models in macroevolutionary studies

### 2015-04-13 Manuscript/ohyou.tex
Minor edits to methods

    where $W(t)$ is drawn at random from a normal distribution with mean $0$ and variance $\sigma^2$. 
    The model assumes that there is no overall drift in the direction of evolution (hence the expectation of $W(t)$ is zero) and that the rate of evolution is constant. 
    Because the direction of change in trait values at each step is random, Brownian motion is often described as a ``random walk''.
    The model assumes the correlation structure among trait values is proportional to the extent of shared ancestry for pairs of species. 
    This means that close relatives will be more similar in their trait values than more distant relatives. It also means that variance in the trait will increase (linearly) in proportion to time. 
    The model has two parameters, the Brownian rate parameter, $\sigma^2$ and the state of the root at time zero, $X(0)$.

@@

    Note that this model has two parameters in addition to those of the Brownian model: $\alpha$ and $\mu$. 
    The parameter $\mu$ is a long-term mean, and it is assumed that species traits evolve around this value. 
    $\alpha$ is the strength of evolutionary force that returns traits back towards the long-term mean if they evolve away from it. 
    $\alpha$ is sometimes referred to as the ``rubber band'' parameter because of the way it pulls traits back towards $\mu$. For more details see the Appendix.

@@

    $\alpha$ can most easily be interpreted by using it to estimate the ``phylogenetic half-life'' ($t_\frac{1}{2}$) of a trait, i.e., the time it takes for a species entering a new niche to evolve halfway toward its new expected optimum \citep{hansen1997stabilizing}, as follows:

@@

    This is sometimes referred to as ``phylogenetic inertia'' but we dislike this term because it means different things to different researchers \citep{Losos:2008aa}.
    If $t_\frac{1}{2}$ is short relative to the branch lengths of the phylogeny, evolution towards the optimum trait value is fast, residual phylogenetic correlations are weak, and there is little influence of the past on trait values \citep{hansen1997stabilizing}.

  \subsection{Known statistical issues with the OU model}
     % Problems with the OU model and where they are reported in the literature?

>>>>

    \noindent
    where $W(t)$ is drawn at random from a normal distribution with mean $0$ and variance $\sigma^2$. 
    The model assumes that there is no overall drift in the direction of evolution (hence the expectation of $W(t)$ is zero) and that the rate of evolution is constant. 
    Because the direction of change in trait values at each step is random, Brownian motion is often described as a ``random walk''.
    The model assumes the correlation structure among trait values is proportional to the extent of shared ancestry for pairs of species. 
    This means that close relatives will be more similar in their trait values than more distant relatives. It also means that variance in the trait will increase (linearly) in proportion to time. 
    The model has two parameters, the Brownian rate parameter, $\sigma^2$ and the state of the root at time zero, $X(0)$.

@@

    \noindent
    Note that this model has two parameters in addition to those of the Brownian model: $\alpha$ and $\mu$. 
    The parameter $\mu$ is a long-term mean, and it is assumed that species traits evolve around this value. 
    $\alpha$ is the strength of evolutionary force that returns traits back towards the long-term mean if they evolve away from it. 
    $\alpha$ is sometimes referred to as the ``rubber band'' parameter because of the way it pulls traits back towards $\mu$. For more details see the Appendix.

@@

    $\alpha$ can more easily be interpreted by using it to estimate the ``phylogenetic half-life'' ($t_\frac{1}{2}$) of a trait, i.e., the time it takes for a species entering a new niche to evolve halfway toward its new expected optimum \citep{hansen1997stabilizing}, as follows:

@@

    \noindent
    This is sometimes referred to as ``phylogenetic inertia'' but we dislike this term because it means different things to different researchers \citep{Losos:2008aa}.
    If $t_\frac{1}{2}$ is short relative to the branch lengths of the phylogeny, evolution towards the optimum trait value is fast, residual phylogenetic correlations are weak, and there is little influence of the past on trait values \citep{hansen1997stabilizing}.

  \subsection{Known statistical issues with the OU model}
  ???Problems with the OU model and where they are reported in the literature?
